Lightning Talk: Software Citation: Process, Principles, and Implementation

### 2016-08-02 meetings/WSSSPE4-lightning-talk/WSSSPE4-lightning-talk.tex
fixing bib items

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2} 
A.~M.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software?citation?principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3} 
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4} 
A.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, “Software Citation Principles,” PeerJ Preprints 4:e2169v2, 2106. \url{https://doi.org/10.7287/peerj.preprints.2169v3}.

>>>>

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2} 
A.~M.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software-citation-principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3} 
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4} 
A.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, “Software Citation Principles,” \textit{PeerJ Preprints} 4:e2169v2, 2106. \url{https://doi.org/10.7287/peerj.preprints.2169v3}.
